lab_notebook

### 2018-12-11 draft_figures.Rmd
"kobe" plots 2012 and 2016 total catch 2012 and 2016

Note: Corbett's ITQ data is only until 2012. Chris's upside data is now updated until 2016 with the more recent RAM data that Dan had. I ran all the figure and regressions under two "scenerios":

    1. until 2012
    2. past 2012. extracted information about which fisheries had ITQs in 2012 and applied it   to the same fisheries into the future. This doesn't take into account other fisheries that   get ITQs in place during that time, or if fisheries stop ITQs

"KOBE" plots with ITQs not updated past 2012
```{r}

@@

F_B_graph <- ggplot(data = f_b_itq, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 5)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))

@@

F_B_graph_updated <- ggplot(data = f_b_itq_updated, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 5)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))

@@

Data until 2012
```{r}
ITQ_projection <- readRDS("data/ITQ_projection.rds")

f_b_itq_countries <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

@@

sum(itq_2012_rightsbasedTURF$Catch, na.rm = TRUE)
#1,301,000
```
2012 total catch:
ITQs: 7,420,003
No ITQ: 142,231
TURF:1,301,000

Data past 2012
```{r}

@@

f_b_itq_countries <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

ITQ_projection_2016 <- ITQ_projection %>%
  filter(Year == "2016") %>%
  select(IdOrig, Country)

itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012, by= c("IdOrig", "Country"), type= "full")

@@

sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
#27,830,933

sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
#266,328,075

sum(itq_2016_rightsbasedTURF$Catch, na.rm = TRUE)
#1505000
```

2016 total catch:
ITQs: 27,830,933
No ITQ: 266,328,075
TURF:1,505,000

>>>>

Notes:
- Corbett's ITQ data is only until 2012. Chris's upside data is now updated until 2016 with the more recent RAM data that Dan had. I ran all the figure and regressions under two "scenerios":

    1. until 2012
    2. past 2012. extracted information about which fisheries had ITQs in 2012 and applied it to the same fisheries into the future. This doesn't take into account other fisheries implement ITQs past 2012, or if fisheries stop ITQs. Only countries with ITQs in 2012 are : Australia, USA, Canda, Japan, Peru, Argentina, South Africa, New Zealand

- for all ITQ related analyzes, limited to fisheries that Corbette had data on. I remove the fisheries that have no information on presence or absence of ITQs. I am unsure if this is biasing the data; should we assume that the fisheries with no information on ITQs have no ITQs or not? This seems like it woud be biased as well. 
    - Corbette's ITQ data includes 375 different fisheries years 1950-2012 for a total of ~15,000 lines of data

"KOBE" plots with ITQs not updated past 2012
All fisheries 1950-2012 
```{r}

@@

f_b_itq$rightsbased[f_b_itq$rightsbased == "0"]<- "No ITQ"
f_b_itq$rightsbased[f_b_itq$rightsbased == "1"]<- "ITQ"

F_B_graph <- ggplot(data = f_b_itq, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 5)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  ggtitle("Fisheries 1950-2012")

@@

f_b_itq_updated$rightsbased[f_b_itq_updated$rightsbased == "0"]<- "No ITQ"
f_b_itq_updated$rightsbased[f_b_itq_updated$rightsbased == "1"]<- "ITQ"

F_B_graph_updated <- ggplot(data = f_b_itq_updated, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 5)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  ggtitle("Fisheries 1950-2016")

@@

###Total Catch ITQ, No ITQ, TURF in 2012
```{r}
ITQ_projection <- readRDS("data/ITQ_projection.rds")

f_b_itq_countries <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
  filter( itq != "NA" & iq != "NA" & ivq != "NA" & turf != "NA") %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

@@

sum(itq_2012_rightsbasedTURF$Catch, na.rm = TRUE)
#1,301,000
```
2012 total catch:
ITQs: 7,420,003
No ITQ: 142,231 (all USA)
TURF:1,301,000 (all Japan)
**note: what units is the catch in the upside/rams data?**

###Total Catch ITQ, No ITQ, TURF in 2016
```{r}

@@

f_b_itq_countries <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
  filter( itq != "NA" & iq != "NA" & ivq != "NA" & turf != "NA") %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

countries_itq_2012_2 <- f_b_itq_countries %>%
  select (Country, rightsbased, Year, IdOrig) %>%
  filter(Year == "2012")  %>%
  select(Country, rightsbased, IdOrig)

ITQ_projection_2016 <- ITQ_projection %>%
  filter(Year == "2016") %>%
  select(IdOrig, Country, Year, Catch)

itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012_2, by= c("IdOrig", "Country"), type= "full")

@@

sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
#26,293,606

sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
#1,154,957

sum(itq_2016_rightsbasedTURF$Catch, na.rm = TRUE)
#382,370.4
```

2016 total catch:
ITQs: 27,830,933
No ITQ: 266,328,075 (all in the USA)
TURF:1,505,000 (all in Japan)

**note: This analyze does not include TURF information from DiscoverTurf GP because that data is not fishery specific enough to merge with the upside/Corbette data**

### 2018-12-11 lab_notebook.Rmd
"kobe" plots 2012 and 2016 total catch 2012 and 2016

FAO website with fisheries data is currently unavaliable. Updated by hand for now; read in below 
```{r}
species_rightsbased <- read_csv("processed_data/species_rightsbased.csv")
```
-	used FAO 3-Alpha species codes (ASFIS) updated 2/2009
-	ones with no ISSCAPP # still are shellfish, snails, crabs, not species specific, common name, species in NA, or a family name with more than 1 #

@@

species_rightsbased <- read_csv("data/species_rightsbased_binary.csv")

@@

join_gdp_rightsbased <- join(gdp, species_rightsbased, by = c("Country"), type = "full")

@@

>>>>

FAO website with fisheries data is currently unavaliable. Updated by hand for now; read in below 
```{r}
species_rightsbased <- read_csv("data/species_rightsbased.csv")

ISSCAAP_species <- select(species_rightsbased, SciName, SpeciesCat)
#write.csv(ISSCAAP_species, file ="ISSCAAP_species.csv")
```
-	used FAO 3-Alpha species codes (ASFIS) updated 2/2009
-	ones with no ISSCAPP # still are shellfish, snails, crabs, not species specific, common name, species in NA, or a family name with more than 1 #

@@

species_rightsbased_binary <- read_csv("data/species_rightsbased_binary.csv")

@@

join_gdp_rightsbased <- join(gdp, species_rightsbased_binary, by = c("Country"), type = "full")

@@

###Need to update the ITQ_projection rds file and the ITQ_projection_updated rds file (1st file is without applying ITQ info past 2012 and the second is)

##ADD THIS INTO THE SCRIPT FOR UPDATING UPSIDE DATA
```{r}
ISSCAAP_species <- read_csv("data/ISSCAAP_species.csv")
ITQ_projection <- readRDS("data/ITQ_projection.rds")

ITQ_projection_isscaap_1 <- join(ISSCAAP_species,ITQ_projection, by = c("SciName", "SpeciesCat"), type = "full" )

ITQ_projection_isscaap <- ITQ_projection_isscaap_1 %>%
  filter(Country != "NA")
